A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Compose

Applies an operation $op$ to two given functions $f_1$ and $f_2$ and returns the
resulting function $f_1\;op\;f_2$. This is the most intuitive function one would
expect when dealing with Boolean functions and it has some interesting properties
too, i.e. the complement of $f_1$ can be computed by setting $f_2$ to \textbf{1}
and $op$ to $\oplus$ (\texttt{XOR}). Moreover, the already mentioned functional
equivalence can be tested by applying $\overline{\oplus}$ (\texttt{XNOR}) to
$f_1$ and $f_2$ for all relevant cases. Therefore, Bryant~\cite{BRYANT92} defined
a function $d(x_1, \ldots, x_n)$ for \textit{Don't cares}:

$d(x_1, \ldots, x_n)=
\begin{cases}
    1, & \text{if values are not relevant} \\
    0, & otherwise
\end{cases}
$

@@

This would result in an algorithm having a worst-case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} ($ITE$)
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) =
f_2 \cdot f_1|_{x_i=1} + \overline{f_2} \cdot f_1|_{x_i=0}
$
\end{center}

@@

This formulation is based upon the fact, that every node $n$ of an OBDD represents
a Boolean function and is denoted by a triple $(var(n), hi(n), lo(n))$. Brace et
al.~\cite{BRACE90} called the variable associated with $n$, i.e. $x_n$ the
\textit{top variable} of $n$.

@@

Bryant~\cite{BRYANT86} also described another, even more efficient way to compose
two function graphs. But this approach only applicable under restricted conditions.
\tbr

>>>>

Applies an operation $op$ to two given functions $f_1$ and $f_2$ and returns the
resulting function $f_1\;op\;f_2$. This is the most intuitive function one would
expect when dealing with Boolean functions and it has some interesting properties
too, i.e. the complement of $f_1$ can be computed by setting $f_2$ to \textbf{1}
and $op$ to $\oplus$ (\texttt{XOR}). Moreover, the already mentioned functional
equivalence can be tested by applying $\overline{\oplus}$ (\texttt{XNOR}) to
$f_1$ and $f_2$ for all relevant cases. Therefore, Bryant~\cite{BRYANT92} defined
a function $d(x_1, \ldots, x_n)$ for \textit{Don't cares}:
\begin{center}
$d(x_1, \ldots, x_n)=
\begin{cases}
    1, & \text{if values are not relevant} \\
    0, & otherwise
\end{cases}
$
\end{center}

@@

This would result in an algorithm having a worst-case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
proposed to extend the \textit{Apply} operation to support ternary operations and
then use the equivalent \textit{if-then-else} ($ITE$) representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) =
f_2 \cdot f_1|_{x_i=1} + \overline{f_2} \cdot f_1|_{x_i=0}
$
\end{center}

@@

This formulation is based upon the fact, that every node $n$ of an OBDD represents
a Boolean function and is denoted by a triple $(var(n), hi(n), lo(n))$.
%Brace et al.~\cite{BRACE90} called the variable associated with $n$ the
%\textit{top variable} of $n$.

@@

Bryant~\cite{BRYANT86} also described another, even more efficient way to compose
two function graphs. But this approach only applicable under restricted conditions.
